%		# in the author/affiliation block all ZIP codes in square brackets removed as it was not %         understood as optional parameter and ZIP codes had bin put in brackets
%abc你好吗？       # References to the current IPAC are changed to "IPAC'19, Melbourne, Australia"
%       # font for ‘url’ style changed to ‘newtxtt’ as it is easier to distinguish "O" and "0"
%
\documentclass[a4paper,
%boxit,        % check whether paper is inside correct margins
%titlepage,    % separate title page
%refpage       % separate references
%biblatex,     % biblatex is used
    keeplastbox,   % flushend option: not to un-indent last line in References
%nospread,     % flushend option: do not fill with whitespace to balance columns
%hyphens,      % allow \url to hyphenate at "-" (hyphens)
%xetex,        % use XeLaTeX to process the file
%luatex,       % use LuaLaTeX to process the file
]{jacow}
%
% ONLY FOR \footnote in table/tabular
%
\usepackage{pdfpages,multirow,ragged2e} %
%
% CHANGE SEQUENCE OF GRAPHICS EXTENSION TO BE EMBEDDED
% ----------------------------------------------------
% test for XeTeX where the sequence is by default eps-> pdf, jpg, png, pdf, ...
%    and the JACoW template provides JACpic2v3.eps and JACpic2v3.jpg which
%    might generates errors, therefore PNG and JPG first
%
\makeatletter%
\ifboolexpr{bool{xetex}}
{\renewcommand{\Gin@extensions}{.pdf,%
    .png,.jpg,.bmp,.pict,.tif,.psd,.mac,.sga,.tga,.gif,%
    .eps,.ps,%
}}{}
\makeatother

% CHECK FOR XeTeX/LuaTeX BEFORE DEFINING AN INPUT ENCODING
% --------------------------------------------------------
%   utf8  is default for XeTeX/LuaTeX
%   utf8  in LaTeX only realises a small portion of codes
%
\ifboolexpr{bool{xetex} or bool{luatex}} % test for XeTeX/LuaTeX
{}                                      % input encoding is utf8 by default
{\usepackage[utf8]{inputenc}}           % switch to utf8

\usepackage[USenglish]{babel}

%
% if BibLaTeX is used
%
\ifboolexpr{bool{jacowbiblatex}}%
{%
    \addbibresource{jacow-test.bib}
    \addbibresource{biblatex-examples.bib}
}{}
\listfiles

%%
%%   Lengths for the spaces in the title
%%   \setlength\titleblockstartskip{..}  %before title, default 3pt
%%   \setlength\titleblockmiddleskip{..} %between title + author, default 1em
%%   \setlength\titleblockendskip{..}    %afterauthor, default 1em

\begin{document}

    \ifboolexpr{bool{jacowbiblatex}}%
    {\printbibliography}%
    {%
    % "biblatex" is not used, go the "manual" way

        \begin{thebibliography}{99}   % Use for  10-99  references
            %\begin{thebibliography}{9} % Use for 1-9 references

            \bibitem{Abada}	A. Abada, M. Abbrescia, S. S. AbdusSalam, et al., M. Benedikt et al. (eds.), “Fcc-ee: The lepton collider,” Eur. Phys. J. Spec. Top., vol. 228, 2019, doi:10.1140/ epjst/e2019-900045-4

            \bibitem{Ogur}	S.Ogur, K.Oide, Y.Papaphilippou, D.Shatilov, and F.Zimmermann, “Bunch Schedules for the FCC-ee Preinjector,” in Proc. 9th International Particle Accelerator Conference (IPAC’18), Vancouver, BC, Canada, April 29-May 4, 2018, Vancouver, BC, Canada, 2018, pp. 79–82, doi:doi:10. 18429/JACoW-IPAC2018-MOPMF001

            \bibitem{shatilov1}	D. Shatilov, “Beam-beam effects at high energy e+e−colliders,” in 62nd ICFA Advanced Beam Dynamics Workshop on High Luminosity Circular e+e− Colliders, 2019, TUYBA02, doi:10.18429/JACoW-eeFACT2018-TUYBA02

            \bibitem{shatilov2}	D.Shatilov,“How to increase the physics output per MW.h for fcc-ee? - parameter optimization for maximum luminosity,” Eur. Phys. J. Plus, vol. 137, no. 1, p. 159, 2022, doi:10. 1140/epjp/s13360-022-02346-x

            \bibitem{Ginzburg} I.F.Ginzburg,G.L.Kotkin,S.L.Panfil,V.G.Serbo,and V. I. Telnov, “Colliding gamma e and gamma gamma beams based on the single pass e+ e- accelerators II. Polarization effects. monochromatization improvement,” Nucl. Instrum. Methods Phys. Res., vol. 219, pp. 5–24, 1984, doi:10.1016/0167-5087(84)90128-5


            \bibitem{Schroeder} D.Schroeder,“Lasers for plasma accelerators,” APS April Meeting, 19 April 2021

            \bibitem{k-bella} “Report of workshop on laser technology for k-bella and beyond, (may 9-11, 2017); kbella workshop report,” 2017, \url{http://www2.lbl.gov/LBL-Programs/atap/Report_ Workshop_kBELLA_laser_tech_final.pdf}

            \bibitem{Kiani} L. Kiani et al., “High average power ultrafast laser technologies for driving future advanced accelerators,” arXiv: 2204.10774, 2022, doi:10.48550/arXiv.2204.10774

            \bibitem{Leemans} W. Leemans, “Laser technology for k-bella and beyond,” Technical Report, Lawrence Berkeley National Laboratory, Tech. Rep., 2017.

            \bibitem{Hofer:IPAC22-WEPOST017} M. Hofer \emph{et al.}, \textquotedblleft{Design of a Collimation Section for the FCC-ee}\textquotedblright, in \emph{Proc. IPAC’22}, Bangkok, Thailand, Jun. 2022, pp. 1722--1725. \url{doi:10.18429/JACoW-IPAC2022-WEPOST017}

            \bibitem{oide_fccis_2022}
            K.~Oide, ``{Collider Optics},'' {\em {FCCIS 2022 Workshop (contributed talk)}}, 2022.

            \bibitem{two_col} Drebot, I., Petrillo, V., and Serafini, L., “Two-colour X-gamma ray inverse Compton back-scattering source”, EPL (Europhysics Letters), vol. 120, no. 1, p. 14002, 2017. doi:10.1209/0295-5075/120/14002.

            \bibitem{XSuite} XSuite, \url{https://github.com/xsuite/xsuite}.

            \bibitem{cain} K. Yokoya, /http://www-acc-theory.kek.jp/members/cainS, (1985).

            \bibitem{collimasim} A. Abramov, et al., "Collimation simulations for the FCC-ee", JINST in publishing.

            \bibitem{geant4} S. Agostinelli, et al., "GEANT4 - a simulation toolkit", Nucl. Instrum. Meth. A 506 (2003) 250-303.

            \bibitem{geant4-2} J. Allison, et al., "Recent Developments in Geant4", Nucl. Instrum. Meth. A 835 (2016) 186-225.

            \bibitem{bdsim} L.J. Nevay et al., "BDSIM: An Accelerator Tracking Code with Particle-Matter Interactions", Computer Physics Communications 252 107200 (2020).

            \bibitem{collimationIPAC23} A. Abramov, {\em et~al.}, ``{Studies of layout and cleaning performance for the FCC-ee collimation system},'' presented at the 14th International Particle Accelerator Conf. (IPAC’23), Venice, Italy, May 2023 paper MOPA128, this conference.

            \bibitem{broggi:ipac23-fcce} G.~Broggi, {\em et~al.}, ``{Beam dynamics studies for the FCC-ee collimation system design},'' presented at the 14th International Particle Accelerator Conf. (IPAC’23), Venice, Italy, May 2023 paper MOPA129, this conference.
        \end{thebibliography}
    }
% end \ifboolexpr
%
% for use as JACoW template the inclusion of the ANNEX parts have been commented out
% to generate the complete documentation please remove the "%" of the next two commands
%
%%%\newpage

%%%\include{annexes-A4}

\end{document}
